\addcontentsline{toc}{chapter}{СПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ}
\begin{thebibliography}{}
    \bibitem{Fast Text Placement Scheme for ASCII Art Synthesis} Chung, Moonjun \& Kwon, Taesoo. (2022). Fast Text Placement Scheme for ASCII Art Synthesis.[Статья] IEEE Access. 10. 1-1. 10.1109/ACCESS.2022.3167567.
    \bibitem{Image-to-ASCII Conversion and Preservation} Engleng, Raj \& D, Ganesh. (2024). Image-to-ASCII Conversion and Preservation.[Статья] International Journal of Innovative Research in Computer and Communication Engineering. 12. 1722-1727. 10.15680/IJIRCCE.2024.1203058.
    \bibitem{Structure-based ASCII Art} Xu, X., Zhang, L., Wong, T. 2010. Structure-based ASCII Art.[Статья] ACM Trans. Graph. 29, 4, Article 52 (July 2010), 9 pages. DOI = 10.1145/1778765.1778789 http://doi.acm.org/10.1145/1778765.1778789.
    \bibitem{Draw methods} Иванова Ю.А. Лекция 8. Методы закраски / Иванова Ю.А. [Электронный ресурс] // Корпоративный портал ТПУ : [сайт]. — URL: https://portal.tpu.ru/SHARED/j/JBOLOTOVA/academic/ComputerGraphics (дата обращения: 19.11.2024).
    \bibitem{Rodgers} Роджерс Д. Алгоритмические основы машинной графики //. — Москва: Мир, 1989.
    \bibitem{Gab} Компьютерная графика. Рейтрейсинг и растеризация. — СПб.: Питер, 2022. — 224 с.: ил. — (Серия «Библиотека программиста»).
    \bibitem{Shading comparison} Shading: Flat vs. Gouraud vs. Phong [Электронный ресурс] Режим доступа: \url{https://www.baeldung.com/cs/shading-flat-vs-gouraud-vs-phong} (дата обращения 13.10.24)
    \bibitem{Invis comparison} SEOUL NATIONAL UNIVERSITY open courseware [Электронный ресурс] Режим доступа: \url{https://ocw.snu.ac.kr/sites/default/files/NOTE/3095.pdf} (дата обращения 13.10.24)
    \bibitem{Future} Anders Carlsson, A. Bill Miller  Future Potentials for ASCII art  [Текст] / Anders Carlsson, A. Bill Miller  // CAC. Paris, France . — 2012. — № 3.
    \bibitem{TUI} Jung-Wei Chen, Jiajie Zhang Comparing Text-based and Graphic User Interfaces for novice and expert users / Jung-Wei Chen, Jiajie Zhang // AMIA Annu Symp Proc. — 2007.
    \bibitem{Fundamentals of cg} Marschner, S. and Shirley, P., 2015. Fundamentals of computer graphics (3rd ed.). CRC Press
    \bibitem{ASCII-hist} Овчинникова А. А., Толоконцева А. С., Валагов Д. А. ПЕРЕКОДИРОВКА И ОБРАБОТКА СТРОК: ОТ ASCII К ANCI/DBCS И UNICODE // Теория и практика современной науки. 2017. №9 (27).
    \bibitem{json} Канаев К.А., Фалеева Е.В., Пономарчук Ю.В. Сравнительный анализ форматов обмена данными, используемых в приложениях с клиент-серверной архитектурой // Фундаментальные исследования. – 2015. – № 2-25. – С. 5569–5572.
    \bibitem{ttf} Haralambous Y. Fonts \& encodings. – "O'Reilly Media, Inc.", 2007.
    \bibitem{go} GO // GO programming language URL: https://go.dev/ (дата обращения: 24.10.2024).
    \bibitem{obj} Murray, James D., Van Ryper, William Encyclopedia of Graphics File Formats / Murray, James D., Van Ryper, William — 2. — : O'Reilly Media, Inc., 1996 — 1158 c.
    \bibitem{tui} tui — Go Terminal UI Framework // URL: https://pkg.go.dev/github.com/hsson/go-tui (дата обращения: 07.12.2024).
    \bibitem{cover} The cover story // The Go Programming Language URL: https://go.dev/blog/cover (дата обращения: 07.12.2024).
    \bibitem{forms}  Yandex Forms /  [Электронный ресурс] // Yandex Cloud : [сайт]. — URL: https://yandex.cloud/ru/docs/forms/ (дата обращения: 22.12.2024).
\end{thebibliography}
